The Country-level Impact of Educational Features on the Rate of Entrepreneurship - Data Gathering and Analysis

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

We look at the average "perceived capabilities" of an individual (18-64) of a given country to start a business.

We also take into account how likely the "fear of failure" could deter the average individual (18-64) of a country to become an entrepreneur.

>>>>

We look at the average "perceived capabilities" of an individual (18-64) of a given country to start a business. The data consists of average percentage at country-level.

We also take into account how the "fear of failure" could deter the average individual (18-64) of a country to become an entrepreneur. The data consists of average percentage at country-level.

##### We will include measures to check how individualistic and group-oriented a given education system is

Literature generally admits that self-confidence partly depends on the integration in social networks. Therefore, as we try to determine how supportive of students' self-esteem a given education system, we will look at how individualistic or group-oriented it is. To quantify such a behavioural feature is not easy, which is why we will have to rely on another measure: how individualistic or group-oriented an average student is by the end of compulsory education. Since OECD PISA collects data about students at the end of compulsory education, we will rely on "the sense of belonging" it defines.
